Coffee Break Experiment #2

### 2022-11-20 cbe2.Rmd
Updated Methods and Results Section

#### Introduction

@@

#### Data

@@

>>>>

**Introduction**

@@

**Data**

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
main <- read_csv("MainSentiment.csv")

main <- main %>% 
  mutate(syuzScore = case_when(syuzhet > 0 ~ "Positive", 
                               syuzhet < 0 ~ "Negative",
                               syuzhet == 0 ~ "Neutral"))
```

**Methods**

To better understand how perception of climate change has changed over time, a sentiment analysis algorithm from the syuzhet^[See https://www.rdocumentation.org/packages/syuzhet/versions/1.0.6] package was applied to the 84,818 tweets across the 4 major fires of interest. The syuzhet package returns sentiment scores in the degree of positively/negativity using a sentiment dictionary developed in the Nebraska Literacy Labs. All links and web addresses were removed from the tweets as well as twitter handles, indicating that the tweet was mentioning or replying to another user. Each tweet was given a sentiment score. Scores above 0 were considered positive, below 0 were negative, and equal to 0 were considered a neutral tweet. Any tweets from twitter accounts with the words "news" or "meteorology" in their biographies were filtered out. We found that most news organization tweets contained neutral, non-opinionated information about the respective wildfire. To control for twitter bots adding unnecessary noise to the data, the users needed to have at least 1 follower and the tweet must be interacted with (like/retweet/comment) at least once.

**Results**

In Figure 1 below, the sentiment classification breakdown is plotted for each of the 4 wildfires. To account for the tweet volume difference between the four fires, percentages of sentiment type is calculated based on the total number of tweets pertaining to a respective fire. The fire are in chronological order, beginning with Tubbs Fire and ending with the Dixie Fire.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3, fig.width=6,fig.cap="Shift in Wildfire Sentiment Over Time."}
main %>%
  filter(!stringr::str_detect(description,'news|meteorology')) %>%
  filter(followers_count > 0 & 
           (like_count > 0 | retweet_count > 0 | quote_count > 0)) %>%
  mutate(fire = fct_relevel(fire, c("Tubbs Fire", 
                      "Camp Fire", 
                      "Bay Area Fire", 
                      "Dixie Fire"))) %>%
  group_by(fire) %>%
  summarize(Positive = length(syuzScore[syuzScore == "Positive"]) / n(),
            Negative = length(syuzScore[syuzScore == "Negative"]) / n(),
            Neutral = length(syuzScore[syuzScore == "Neutral"]) / n()) %>%
  gather(sentiment, percentage, Positive:Neutral) %>%
  ggplot(aes(x = fire, y = percentage, fill = sentiment)) +
  geom_bar(stat = "identity", position = "dodge") + 
  scale_fill_manual(values = c("red2", "blue", "darkgreen")) + 
  theme_bw() +
  labs(title = "Wildfire Sentiment Change Over Time",
       x = "",
       y = "Percentage",
       fill = "Sentiment")
```

Even though the tweet volume is not consistent throughout time, figure 1 gives us preliminary evidence that there may a shift in tweet sentiment as we observe more and more of these natural disasters. Beginning with Camp Fire, the amount of negative tweets has been steadily increasing for each wildfire.

**Discussion**
